### 2024-09-12 cognitive-bias.qmd
20240911 - additions

Below, we provide examples of [heuristics](#sec-heuristics), [*cognitive biases*](#sec-cognitiveBiases), and [*fallacies*](#sec-fallacies).

@@

The confidence that people tend to have in their predictions depends less and the quantity and quality of the evidence for their predictions and more on the quality of the narrative they can tell about the (little) information they have immediate access to [@Kahneman2011].
For instance, people tend not to consider other relevant, important factors that they do not have immediate access to, consistent with the [WYSIATI heuristic](#sec-heuristicsWYSIATI).
Instead, people tend to focus on the cohesiveness and plausibility of the story, which differs from its probability [@Kahneman2011].

@@

*Hindsight bias* is the tendency to perceive that past events were more predictable than they were (i.e., the "I-knew-it-all-along" effect).
People tend to remember the succeess of their predictions and forget the failures of their predictions.
For instance, if a third-string Quarterback has a breakout game, a fantasy manager may claim that they "knew it all along" that the player was going to breakout, despite not having picked up the player.
That same manager may forget the many other predictions they had that did not come true.

>>>>

Below, we provide examples of [heuristics](#sec-heuristics), [*cognitive biases*](#sec-cognitiveBiases), and [*fallacies*](#sec-fallacies).
These are not exhaustive lists of all the [heuristics](#sec-heuristics), [*cognitive biases*](#sec-cognitiveBiases), and [*fallacies*](#sec-fallacies).
They are some examples of key ones that are relevant fantasy football.

@@

The confidence that people tend to have in their predictions depends less and the quantity and quality of the evidence for their predictions and more on the quality of the narrative they can tell about the (little) information they have immediate access to [@Kahneman2011].
For instance, people tend not to consider other relevant, important factors that they do not have immediate access to, consistent with the [WYSIATI heuristic](#sec-heuristicsWYSIATI).
Instead, people tend to focus on the coherence and plausibility of the story, which differs from its probability [@Kahneman2011].
That is, one's confidence is not necessarily related to the likelihood that the judgment is correct—it often reflects the "illusion of validity" [@Kahneman2011].
As one gains more knowledge in a domain, the person also tends to become unrealistically overconfident in their ability to make accurate judgments and predictions [@Kahneman2011].

@@

*Hindsight bias* is the tendency to perceive that past events were more predictable than they were (i.e., the "I-knew-it-all-along" effect).
Everything seems to make sense in hindsight [@Kahneman2011].
People tend to remember the succeess of their predictions and forget the failures of their predictions.
For instance, if a third-string Quarterback has a breakout game, a fantasy manager may claim that they "knew it all along" that the player was going to breakout, despite not having picked up the player.
That same manager may forget the many other predictions they had that did not come true.
